---
title: "Data of members of Toronto City Council - Voting Recorde"
author: 
  - Che-Yu Wang
thanks: "Code and data are available at: https://github.com/Cheyuwang/Toronto-data-analysis-/tree/main/input%20/skatches."
date: 2024/01/22
date-format: long
abstract: "This study examines the voting records of Toronto City Council members from 2018 to 2022, a period highlighted by substantial political and social changes. The dataset is used to calculate voting trends, attendance, and council member alignment. This study uses substantial data processing and analysis to uncover voting patterns and council political dynamics. The analysis focuses on decision-making tendencies, important votes, and the relationships between council members' votes and political factors. These findings provide insight into Toronto municipal governance, enriching local politics. "
format: pdf
number-sections: true
bibliography: references.bib
---

# Introduction

This study examines the voting behaviors of Toronto City Council members from 2018 to 2022, focusing on their participation rates, vote results and external factors influencing voting decisions. The analysis uses a dataset in R studio [@citeR] and rigorous data cleaning, transformation, and statistical techniques to interpret complex voting patterns. However, the analysis will also incudes tables and bar chart. The study's goal is to determine the consistency and variety in members participation and decisions, as well as to identify any links between voting patterns and political affiliations or external influences. 




```{r}
#| echo: false
#| warning: false
#| message: false
#| tbl-cap: Voting results
#| label: tbl-voting

### Working setup
#install.packages("here")

#### Acquire #### 
library(knitr)
library(tidyverse)
library(janitor) # Load the 'janitor' library for 'clean_names()'
# Data sources 2.3.3 https://tellingstorieswithdata.com/02-drinking_from_a_fire_hose.html 
# Regenerate the dataset by each person's voting results 
# Load the data and show the column names

voting_record <- read_csv(
  here::here("outputs/data/processed_voting_record_clean.csv"), # Correct usage of 'here' function
  show_col_types = FALSE
) # Added closing parenthesis


# Process the data - adjust this part based on your dataset
# Assuming there are columns named 'First Name', 'Last Name', and 'Vote'
voting_summary <- voting_record %>%
  unite("Member", `first_name`, `last_name`, sep = " ") %>%
  filter(vote == "Yes") %>%
  count(Member) %>%
  arrange(-n) %>%
  slice(1:5)

kable(voting_summary)
```



refer to @fig_1  Source 2.33 [@alexander2023telling]

```{r}
#| echo: false
#| warning: false
#| message: false
#| fig-cap: Voting results
#| label: fig-voting
#| 
# Create the bar chart
ggplot(voting_summary, aes(x = Member, y = n)) +
  geom_bar(stat = "identity", fill = "blue") +
  labs(
    title = "Count of 'Yes' Votes by Toronto City Council Members",
    x = "Council Member",
    y = "Number of 'Yes' Votes"
  ) +
  theme_minimal() 
```
Figure.1 

# Data {#sec-data}

In this cases, since their's multiple voting results, I picked the five highest voting results from the multiple candidate. However, we can conclude that the gap between the five highest voting results for candidate are really close, so is mean the term "close candidate votes" refers to an election outcome in which the leading candidates obtain almost identical numbers of votes, resulting in a tight margin of victory. @tbl-voting @fig-voting 

The way I created this table by the [@knitr]  to created the table and bar chart. From the Bar plot firgure 1, we see the the same results from the tables that Mike Layton having highest votes in this election. 



\newpage


# References

[@citeR]
[@janitor]
[@opendatatoronto]



